---
title: "scRNA-seq Report for dataset: `r basename(params$app_data$user_inputs$dataset)`"
# author: "Generated from Shiny Application"
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 10
    fig_height: 6
params:
  app_data: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                     fig.align = 'center', out.width = '100%')
library(knitr)
library(DT)

# Access parameters
saved_plots <- params$app_data$saved_plots
canvas_info <- params$app_data$canvas_info
user_inputs <- params$app_data$user_inputs
timestamp <- params$app_data$timestamp
```

**Generated on:** `r format(timestamp, "%Y-%m-%d %H:%M:%S")`

The [Bioinformatics Resource Center](https://rockefelleruniversity.github.io/) scRNA-seq Browser provides an interactive platform for exploring single-cell RNA sequencing data. This report summarizes the key visualizations and analyses performed during your session.

This report was written by [George Muñoz](https://github.com/george123ya) at the Rockefeller University Bioinformatics Resource Center with contributions by [Luis Soto-Ugaldi](https://github.com/SotoLF), [Doug Barrows](https://github.com/dougbarrows) and [Thomas Carroll](https://github.com/ThomasCarroll) from the BRC.

## Visualization Results

```{r heatmap-section-header, eval=!is.null(saved_plots$heatmap1) || !is.null(saved_plots$heatmap2), results='asis'}
cat("### Heatmap Visualizations\n\n")
```

```{r heatmap1-header, eval=!is.null(saved_plots$heatmap1), results='asis'}
cat("#### Individual Genes\n\n")
```

```{r heatmap1-details, eval=!is.null(saved_plots$heatmap1), results='asis'}
if(!is.null(user_inputs$heatmap_genes_panel1)) {
  cat("**Input Parameters:**\n\n")
  cat("- **Genes:**", user_inputs$heatmap_genes_panel1, "\n")
  cat("- **Score Type:**", user_inputs$heatmap_score_panel1, "\n")
  cat("- **Cell Grouping Mode:**", user_inputs$heatmap_cell_group_mode_panel1, "\n")
  cat("- **Cluster/Color By:**", ifelse(is.null(user_inputs$heatmap_cluster_by_panel1), "None", user_inputs$heatmap_cluster_by_panel1), "\n\n")
  
  cat("**Reproducible Code:**\n\n")
  cat("```r\n")
  cat("# Load analysis functions\n")
  cat("source('https://github.com/george123ya/scRNAseq_Visualizer/blob/main/modules/reproducible_functions.R?raw=true')\n\n")
  
  cat("# Initialize data connection\n")
  cat(paste0("zarr_file <- '", ifelse(grepl("^https?://", user_inputs$dataset), user_inputs$dataset, "path/to/your/dataset.zarr"), "'  # or .h5ad file\n"))
  cat("lazy_data <- init_fast_zarr_h5ad(zarr_file)\n\n")
  
  cat("# Process genes for Panel 1\n")
  # Clean up genes and remove empty strings, then format properly
  genes_clean <- trimws(unlist(strsplit(user_inputs$heatmap_genes_panel1, ",|\\s+")))
  genes_clean <- genes_clean[genes_clean != "" & !is.na(genes_clean)]
  cat("genes <- c(", paste(paste0("\"", genes_clean, "\""), collapse = ", "), ")\n")
  cat("genes <- toupper(trimws(genes))\n")
  cat("genes <- genes[genes %in% toupper(lazy_data$genes)]\n\n")
  
  cat("# Extract expression data\n")
  cat("expr_mat <- lazy_data$get_genes_expression_batch(genes, layer='X')\n")
  cat("if(is.null(expr_mat)) {\n")
  cat("  mat <- matrix(NA, nrow=lazy_data$n_cells, ncol=length(genes))\n")
  cat("  colnames(mat) <- genes\n")
  cat("} else {\n")
  cat("  mat <- expr_mat\n")
  cat("}\n\n")
  
  cat("# Process heatmap data\n")
  cat("heatmap_data <- process_heatmap_data(\n")
  cat("  mat=mat,\n")
  cat(paste0("  score_type=\"", user_inputs$heatmap_score_panel1, "\",\n"))
  cat(paste0("  cell_group_mode=\"", user_inputs$heatmap_cell_group_mode_panel1, "\",\n"))
  cat(paste0("  cluster_by=\"", ifelse(is.null(user_inputs$heatmap_cluster_by_panel1), "", user_inputs$heatmap_cluster_by_panel1), "\"\n"))
  cat(")\n\n")
  
  cat("# Generate heatmap\n")
  cat("heatmap_plot <- render_heatmap(heatmap_data, \"Panel 1: Individual Genes\")\n")
  cat("print(heatmap_plot)\n")
  cat("```\n\n")
  
  cat("🔗 **Functions Source:** https://github.com/george123ya/scRNAseq_Visualizer/blob/main/modules/reproducible_functions.R\n\n")
}
```

```{r heatmap1-plot, eval=!is.null(saved_plots$heatmap1)}
include_graphics(normalizePath(saved_plots$heatmap1))
```

```{r heatmap2-header, eval=!is.null(saved_plots$heatmap2), results='asis'}
cat("#### Gene Sets / Pathways\n\n")
```

```{r heatmap2-details, eval=!is.null(saved_plots$heatmap2), results='asis'}
if(!is.null(user_inputs$heatmap_gene_group_mode_panel2)) {
  cat("**Input Parameters:**\n\n")
  cat("- **Gene Group Mode:**", user_inputs$heatmap_gene_group_mode_panel2, "\n")
  cat("- **Score Type:**", user_inputs$heatmap_score_panel2, "\n")
  cat("- **Cell Grouping Mode:**", user_inputs$heatmap_cell_group_mode_panel2, "\n")
  cat("- **Cluster/Color By:**", ifelse(is.null(user_inputs$heatmap_cluster_by_panel2), "None", user_inputs$heatmap_cluster_by_panel2), "\n")
  
  # Show specific selections based on mode
  if(user_inputs$heatmap_gene_group_mode_panel2 == "pathways" && !is.null(user_inputs$heatmap_pathway_select_panel2)) {
    cat("- **Selected Pathways:**", paste(user_inputs$heatmap_pathway_select_panel2, collapse=", "), "\n")
  } else if(user_inputs$heatmap_gene_group_mode_panel2 == "custom_gmt" && !is.null(user_inputs$heatmap_gmt_sets_panel2)) {
    cat("- **Selected GMT Gene Sets:**", paste(user_inputs$heatmap_gmt_sets_panel2, collapse=", "), "\n")
  } else if(user_inputs$heatmap_gene_group_mode_panel2 == "manual" && !is.null(user_inputs$selected_manual_genesets)) {
    cat("- **Selected Manual Gene Sets:**", paste(user_inputs$selected_manual_genesets, collapse=", "), "\n")
  }
  cat("\n")
  
  cat("**Reproducible Code:**\n\n")
  cat("```r\n")
  cat("# Load analysis functions\n")
  cat("source('https://raw.githubusercontent.com/george123ya/scRNAseq_Visualizer/main/modules/reproducible_functions.R')\n\n")
  
  cat("# Initialize data connection\n")
  cat(paste0("zarr_file <- '", ifelse(grepl("^https?://", user_inputs$dataset), user_inputs$dataset, "path/to/your/dataset.zarr"), "'  # or .h5ad file\n"))
  cat("lazy_data <- init_fast_zarr_h5ad(zarr_file)\n\n")
  
  if(user_inputs$heatmap_gene_group_mode_panel2 == "pathways") {
    cat("# Load pathway data\n")
    cat("pathways <- lazy_data$pathways\n")
    if("ALL" %in% user_inputs$heatmap_pathway_select_panel2) {
      cat("gene_groups <- pathways  # All pathways selected\n")
    } else {
      cat("selected_pathways <- c(", paste(paste0("\"", user_inputs$heatmap_pathway_select_panel2, "\""), collapse=","), ")\n")
      cat("gene_groups <- pathways[selected_pathways]\n")
    }
  } else if(user_inputs$heatmap_gene_group_mode_panel2 == "custom_gmt") {
    cat("# Load GMT file\n")
    cat("gmt_data <- parse_gmt_file('path/to/your/geneset.gmt')\n")
    if("ALL" %in% user_inputs$heatmap_gmt_sets_panel2) {
      cat("gene_groups <- gmt_data  # All GMT gene sets selected\n")
    } else {
      cat("selected_gmt <- c(", paste(paste0("\"", user_inputs$heatmap_gmt_sets_panel2, "\""), collapse=","), ")\n")
      cat("gene_groups <- gmt_data[selected_gmt]\n")
    }
  } else if(user_inputs$heatmap_gene_group_mode_panel2 == "manual") {
    cat("# Define manual gene sets\n")
    cat("manual_genesets <- list(\n")
    if(!is.null(user_inputs$selected_manual_genesets)) {
      for(i in seq_along(user_inputs$selected_manual_genesets)) {
        cat("  \"", user_inputs$selected_manual_genesets[i], "\"=c(\"GENE1\",\"GENE2\",\"GENE3\")")
        if(i < length(user_inputs$selected_manual_genesets)) cat(",")
        cat("\n")
      }
    }
    cat(")\n")
    cat("gene_groups <- manual_genesets\n")
  }
  
  cat("\n# Calculate gene set scores and create heatmap\n")
  cat("heatmap_data <- calculate_geneset_scores(\n")
  cat("  lazy_data=lazy_data,\n")
  cat("  gene_groups=gene_groups,\n")
  cat("  score_type=\"", user_inputs$heatmap_score_panel2, "\",\n")
  cat("  cell_group_mode=\"", user_inputs$heatmap_cell_group_mode_panel2, "\",\n")
  cat("  cluster_by=\"", ifelse(is.null(user_inputs$heatmap_cluster_by_panel2), "", user_inputs$heatmap_cluster_by_panel2), "\"\n")
  cat(")\n\n")
  
  cat("# Generate heatmap\n")
  cat("heatmap_plot <- render_heatmap(heatmap_data, \"Panel 2: Gene Sets\")\n")
  cat("print(heatmap_plot)\n")
  cat("```\n\n")
  
  cat("🔗 **Functions Source:** https://github.com/george123ya/scRNAseq_Visualizer/blob/main/modules/reproducible_functions.R\n\n")
}
```

```{r heatmap2-plot, eval=!is.null(saved_plots$heatmap2)}
include_graphics(normalizePath(saved_plots$heatmap2))
```


```{r gene-section-header, eval=!is.null(saved_plots$gene_main), results='asis'}
cat("### Gene Expression Analysis\n\n")
```

```{r gene-analysis-header, eval=!is.null(saved_plots$gene_main), results='asis'}
cat("#### Main Gene Analysis Plot\n\n")
```

```{r gene-plot-details, eval=!is.null(saved_plots$gene_main), results='asis'}
if(!is.null(user_inputs$geneSearch_tab)) {
  cat("**Input Parameters:**\n\n")
  cat("- **Selected Genes:**", paste(user_inputs$geneSearch_tab, collapse=", "), "\n")
  cat("- **Group By:**", user_inputs$gene_group_by, "\n")
  cat("- **Plot Type:**", user_inputs$gene_plot_type, "\n")
  cat("- **Show Points:**", user_inputs$gene_show_points, "\n")
  cat("- **Point Size:**", user_inputs$gene_point_size, "\n")
  cat("- **Log Scale:**", user_inputs$gene_log_scale, "\n\n")
  
  cat("**Reproducible Code:**\n\n")
  cat("```r\n")
  cat("# Load required libraries\n")
  cat("library(ggplot2)\n")
  cat("library(reshape2)\n\n")
  
  cat("# Load analysis functions\n")
  cat("source('https://raw.githubusercontent.com/george123ya/scRNAseq_Visualizer/main/modules/reproducible_functions.R')\n\n")
  
  cat("# Initialize data connection\n")
  cat(paste0("zarr_file <- '", ifelse(grepl("^https?://", user_inputs$dataset), user_inputs$dataset, "path/to/your/dataset.zarr"), "'  # or .h5ad file\n"))
  cat("lazy_data <- init_fast_zarr_h5ad(zarr_file)\n\n")
  
  cat("# Define selected genes\n")
  genes_clean <- trimws(user_inputs$geneSearch_tab)
  genes_clean <- genes_clean[genes_clean != "" & !is.na(genes_clean)]
  cat("genes <- c(", paste(paste0("\"", genes_clean, "\""), collapse = ", "), ")\n")
  cat("genes <- toupper(trimws(genes))\n")
  cat("genes <- genes[genes %in% toupper(lazy_data$genes)]\n\n")
  
  cat("# Extract expression data\n")
  cat("expr_list <- lapply(genes, function(g) {\n")
  cat("  lazy_data$get_gene_expression(gene_name = g)\n")
  cat("})\n")
  cat("mat <- do.call(cbind, expr_list)\n")
  cat("colnames(mat) <- genes\n\n")
  
  cat("# Get grouping variable\n")
  cat("group_var <- lazy_data$get_obs_column(lazy_data$z, \"", user_inputs$gene_group_by, "\")\n")
  cat("group_var <- as.factor(group_var)\n\n")
  
  cat("# Build long-format data frame\n")
  cat("df <- data.frame(group = group_var, mat)\n")
  cat("long_df <- reshape2::melt(df, id.vars = \"group\", variable.name = \"gene\", value.name = \"expression\")\n\n")
  
  cat("# Generate plot\n")
  cat("p <- ggplot(long_df, aes(x = group, y = expression, fill = group)) +\n")
  cat("  facet_wrap(~ gene, scales = \"free_y\") +\n")
  cat("  labs(x = \"Group\", y = \"Expression Level\") +\n")
  cat("  theme_minimal() +\n")
  cat("  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = \"none\")\n\n")
  
  cat("# Add plot layer\n")
  if(user_inputs$gene_plot_type == "violin") {
    cat("p <- p + geom_violin(scale = \"width\", trim = TRUE)\n")
  } else {
    cat("p <- p + geom_boxplot(outlier.size = 0.5)\n")
  }
  
  if(user_inputs$gene_show_points) {
    cat("p <- p + geom_jitter(size = ", user_inputs$gene_point_size, ", width = 0.2, alpha = 0.5)\n")
  }
  
  if(user_inputs$gene_log_scale) {
    cat("p <- p + scale_y_continuous(trans = \"log1p\")\n")
  }
  
  cat("p <- p + labs(title = \"", ifelse(user_inputs$gene_plot_type == "violin", "Gene Expression (Violin Plot)", "Gene Expression (Box Plot)"), "\")\n\n")
  
  cat("# Display plot\n")
  cat("print(p)\n")
  cat("```\n\n")
  
  cat("🔗 **Functions Source:** https://github.com/george123ya/scRNAseq_Visualizer/blob/main/modules/reproducible_functions.R\n\n")
}
```

```{r gene-analysis-plot, eval=!is.null(saved_plots$gene_main)}
include_graphics(normalizePath(saved_plots$gene_main))
```

```{r gene-analysis-text, eval=!is.null(saved_plots$gene_main), results='asis'}
cat("\n\nThis plot shows the main gene expression analysis results.\n")
```

```{r violin-plots-header, eval=length(params$app_data$violin_genes) > 0, results='asis'}
cat("#### Individual Gene Violin Plots\n\n")
```

```{r violin-plots, eval=length(params$app_data$violin_genes) > 0, results='asis'}
if (length(params$app_data$violin_genes) > 0) {
  for (gene in params$app_data$violin_genes) {
    plot_name <- paste0("violin_", gene)
    if (!is.null(params$app_data$saved_plots[[plot_name]])) {
      cat(sprintf("##### %s\n", gene))
      cat(sprintf("![%s](%s){width=80%%}\n\n", plot_name, normalizePath(params$app_data$saved_plots[[plot_name]])))
    }
  }
} else {
  cat("No individual violin plots available.\n\n")
}
```

```{r qc-section-header, eval=!is.null(saved_plots$qc_main), results='asis'}
cat("### Quality Control\n\n")
```

```{r qc-analysis-header, eval=!is.null(saved_plots$qc_main), results='asis'}
cat("#### Quality Control Plot\n\n")
```

```{r qc-plot-details, eval=!is.null(saved_plots$qc_main), results='asis'}
if(!is.null(user_inputs$qc_plot_type)) {
  cat("**Input Parameters:**\n\n")
  cat("- **Plot Type:**", user_inputs$qc_plot_type, "\n")
  if(user_inputs$qc_plot_type == "scatter") {
    cat("- **X Metric:**", user_inputs$qc_x_metric, "\n")
    cat("- **Y Metric:**", user_inputs$qc_y_metric, "\n")
    cat("- **Color By:**", ifelse(is.null(user_inputs$qc_color_by) || user_inputs$qc_color_by == "None", "None", user_inputs$qc_color_by), "\n")
  } else {
    cat("- **Metric:**", user_inputs$qc_metric, "\n")
    cat("- **Group By:**", user_inputs$qc_group_by, "\n")
  }
  cat("- **Show Points (Violin/Box):**", user_inputs$qc_show_points, "\n")
  cat("- **Point Size:**", user_inputs$qc_point_size, "\n")
  cat("- **Log Scale:**", user_inputs$qc_log_scale, "\n\n")
  
  cat("**Reproducible Code:**\n\n")
  cat("```r\n")
  cat("# Load required libraries\n")
  cat("library(ggplot2)\n\n")
  
  cat("# Load analysis functions\n")
  cat("source('https://raw.githubusercontent.com/george123ya/scRNAseq_Visualizer/main/modules/reproducible_functions.R')\n\n")
  
  cat("# Initialize data connection\n")
  cat(paste0("zarr_file <- '", ifelse(grepl("^https?://", user_inputs$dataset), user_inputs$dataset, "path/to/your/dataset.zarr"), "'  # or .h5ad file\n"))
  cat("lazy_data <- init_fast_zarr_h5ad(zarr_file)\n\n")
  
  if(user_inputs$qc_plot_type == "scatter") {
    cat("# Prepare data for scatter plot\n")
    cat("x <- as.numeric(lazy_data$get_obs_column(lazy_data$z, \"", user_inputs$qc_x_metric, "\"))\n")
    cat("y <- as.numeric(lazy_data$get_obs_column(lazy_data$z, \"", user_inputs$qc_y_metric, "\"))\n")
    if(!is.null(user_inputs$qc_color_by) && user_inputs$qc_color_by != "None") {
      cat("color <- as.factor(lazy_data$get_obs_column(lazy_data$z, \"", user_inputs$qc_color_by, "\"))\n")
      cat("dat <- data.frame(X = x, Y = y, Color = color)\n")
    } else {
      cat("dat <- data.frame(X = x, Y = y)\n")
    }
    cat("if(nrow(dat) > 50000) {\n")
    cat("  set.seed(123)\n")
    cat("  dat <- dat[sample(nrow(dat), 50000), ]\n")
    cat("}\n\n")
    
    cat("# Generate scatter plot\n")
    cat("p <- ggplot(dat, aes(x = X, y = Y))\n")
    if(!is.null(user_inputs$qc_color_by) && user_inputs$qc_color_by != "None") {
      cat("p <- p + aes(color = Color)\n")
    }
    cat("p <- p + geom_point(alpha = 0.5, size = ", user_inputs$qc_point_size, ") +\n")
    cat("  labs(title = \"", user_inputs$qc_x_metric, " vs ", user_inputs$qc_y_metric, "\",\n")
    cat("       x = \"", user_inputs$qc_x_metric, "\",\n")
    cat("       y = \"", user_inputs$qc_y_metric, "\") +\n")
    cat("  theme_minimal()\n")
    if(user_inputs$qc_log_scale) {
      cat("p <- p + scale_x_log10() + scale_y_log10()\n")
    }
  } else {
    cat("# Prepare data for violin/box/histogram plot\n")
    cat("metric <- as.numeric(lazy_data$get_obs_column(lazy_data$z, \"", user_inputs$qc_metric, "\"))\n")
    cat("group <- as.factor(lazy_data$get_obs_column(lazy_data$z, \"", user_inputs$qc_group_by, "\"))\n")
    cat("dat <- data.frame(Metric = metric, Group = group)\n")
    cat("if(", user_inputs$qc_show_points, " && nrow(dat) > 20000) {\n")
    cat("  set.seed(123)\n")
    cat("  dat_points <- dat[sample(nrow(dat), 20000), ]\n")
    cat("} else {\n")
    cat("  dat_points <- dat\n")
    cat("}\n\n")
    
    cat("# Generate plot\n")
    if(user_inputs$qc_plot_type == "violin") {
      cat("p <- ggplot(dat, aes(x = Group, y = Metric, fill = Group)) +\n")
      cat("  geom_violin(trim = FALSE)\n")
      if(user_inputs$qc_show_points) {
        cat("p <- p + geom_jitter(data = dat_points, width = 0.2, alpha = 0.4, size = ", user_inputs$qc_point_size, ")\n")
      }
    } else if(user_inputs$qc_plot_type == "box") {
      cat("p <- ggplot(dat, aes(x = Group, y = Metric, fill = Group)) +\n")
      cat("  geom_boxplot()\n")
      if(user_inputs$qc_show_points) {
        cat("p <- p + geom_jitter(data = dat_points, width = 0.2, alpha = 0.4, size = ", user_inputs$qc_point_size, ")\n")
      }
    } else if(user_inputs$qc_plot_type == "histogram") {
      cat("p <- ggplot(dat, aes(x = Metric, fill = Group)) +\n")
      cat("  geom_histogram(position = \"identity\", alpha = 0.5, bins = 50)\n")
    }
    cat("p <- p + theme_minimal() +\n")
    cat("  labs(title = \"QC Metric: ", user_inputs$qc_metric, "\",\n")
    cat("       x = \"", user_inputs$qc_group_by, "\",\n")
    cat("       y = \"", user_inputs$qc_metric, "\")\n")
    if(user_inputs$qc_log_scale) {
      cat("p <- p + scale_y_log10()\n")
    }
  }
  
  cat("# Display plot\n")
  cat("print(p)\n")
  cat("```\n\n")
  
  cat("🔗 **Functions Source:** https://github.com/george123ya/scRNAseq_Visualizer/blob/main/modules/reproducible_functions.R\n\n")
}
```

```{r qc-analysis-plot, eval=!is.null(saved_plots$qc_main)}
include_graphics(normalizePath(saved_plots$qc_main))
```

```{r qc-analysis-text, eval=!is.null(saved_plots$qc_main), results='asis'}
cat("\n\nThis plot displays the quality control metrics for the analysis.\n")
```

```{r canvas-section-header, results='asis'}
# Check if any canvas plots exist
canvas_plots <- saved_plots[grepl("canvas", names(saved_plots))]
if(length(canvas_plots) > 0) {
  cat("## Interactive Canvas Elements\n\n")
}
```

```{r scatterplot-canvas-header, eval=!is.null(saved_plots$scatterplot_canvas), results='asis'}
cat("### Scatterplot Canvas\n\n")
cat("#### Scatterplot Canvas\n\n")
```

```{r scatterplot-canvas-plot, eval=!is.null(saved_plots$scatterplot_canvas)}
include_graphics(normalizePath(saved_plots$scatterplot_canvas))
```

```{r scatterplot-canvas-text, eval=!is.null(saved_plots$scatterplot_canvas), results='asis'}
cat("\n\nThis image represents a static snapshot of the interactive scatterplot canvas generated in the application.\n")
```

```{r gene-canvas-header, results='asis'}
gene_canvases <- saved_plots[grepl("^gene_canvas_", names(saved_plots))]
if(length(gene_canvases) > 0) {
  cat("### Gene-Specific Canvas Plots\n\n")
  cat("The following static images represent snapshots of the interactive gene-specific canvas plots generated in the application:\n\n")
}
```

```{r gene-canvas-plots, results='asis'}
gene_canvases <- saved_plots[grepl("^gene_canvas_", names(saved_plots))]
if(length(gene_canvases) > 0) {
  for(canvas_name in names(gene_canvases)) {
    gene_name <- gsub("gene_canvas_", "", canvas_name)
    cat(sprintf("#### %s\n\n", gene_name))
    
    # Create a temporary variable for the current plot path
    current_plot <- gene_canvases[[canvas_name]]
    
    # Output the image using markdown syntax within asis
    cat(sprintf("![](%s)\n\n", normalizePath(current_plot)))
    
    cat(sprintf("This image represents a static snapshot of the interactive canvas for gene %s.\n\n", gene_name))
  }
}
```

## Data Processing Summary

```{r processing-summary, results='asis'}
total_plots <- length(saved_plots)
total_canvases <- length(saved_plots[grepl("^scatterplot_canvas|^gene_canvas_", names(saved_plots))])

cat("### Analysis Summary\n\n")
cat("- **Static plots generated (including canvas snapshots):** ", total_plots, "\n")
cat("- **Interactive canvases captured:** ", total_canvases, "\n")
cat("- **Report generation time:** ", format(timestamp, "%Y-%m-%d %H:%M:%S"), "\n\n")
```

## Technical Information

```{r tech-info}
cat("### Session Information\n\n")
cat("R version:", R.version.string, "\n")
cat("Platform:", R.version$platform, "\n")
cat("Report generated using: rmarkdown and knitr\n")
```

---

*This report was automatically generated from your Shiny application. For interactive features and real-time updates, please return to the application interface.*