---
title: "scRNA-seq Report for dataset: `r basename(params$app_data$user_inputs$dataset)`"
# author: "Generated from Shiny Application"
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    toc: true
    toc_float: true
    code_folding: hide
    fig_width: 10
    fig_height: 6
params:
  app_data: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                     fig.align = 'center', out.width = '100%')
library(knitr)
library(DT)

# Access parameters
saved_plots <- params$app_data$saved_plots
canvas_info <- params$app_data$canvas_info
user_inputs <- params$app_data$user_inputs
timestamp <- params$app_data$timestamp
```

**Generated on:** `r format(timestamp, "%Y-%m-%d %H:%M:%S")`

The [Bioinformatics Resource Center](https://rockefelleruniversity.github.io/) scRNA-seq Browser provides an interactive platform for exploring single-cell RNA sequencing data. This report summarizes the key visualizations and analyses performed during your session.

This report was written by [George Muñoz](https://github.com/george123ya) at the Rockefeller University Bioinformatics Resource Center with contributions by [Luis Soto-Ugaldi](https://github.com/SotoLF), [Doug Barrows](https://github.com/dougbarrows) and [Thomas Carroll](https://github.com/ThomasCarroll) from the BRC.

## Visualization Results

```{r heatmap-section-header, results='asis'}
heatmap_count <- sum(c(!is.null(saved_plots$heatmap1), !is.null(saved_plots$heatmap2)))

if(heatmap_count > 0) {
  cat("### Heatmap Analysis\n\n")
  cat("The following heatmap visualizations were generated:\n\n")
}
```

```{r heatmap1-header, eval=!is.null(saved_plots$heatmap1), results='asis'}
cat("#### Heatmap 1 - Individual Genes\n\n")
```

```{r heatmap1-details, eval=!is.null(saved_plots$heatmap1), results='asis'}
if(!is.null(user_inputs$heatmap_genes_panel1)) {
  cat("**Input Parameters:**\n\n")
  cat("- **Genes:** ", user_inputs$heatmap_genes_panel1, "\n")
  cat("- **Score Type:** ", user_inputs$heatmap_score_panel1, "\n")
  cat("- **Cell Grouping Mode:** ", user_inputs$heatmap_cell_group_mode_panel1, "\n")
  cat("- **Cluster/Color By:** ", ifelse(is.null(user_inputs$heatmap_cluster_by_panel1), "None", user_inputs$heatmap_cluster_by_panel1), "\n\n")
  
  cat("**Reproducible Code:**\n\n")
  cat("```r\n")
  cat("# Install and load the analysis package\n")
  cat("devtools::install_github('yourusername/yourrepo')\n")
  cat("library(yourpackagename)  # This loads ComplexHeatmap and other dependencies\n\n")
  
  cat("# Initialize data connection\n")
  cat("zarr_file <- 'path/to/your/dataset.zarr'  # or .h5ad file\n")
  cat("lazy_data <- init_fast_zarr_h5ad(zarr_file)\n\n")
  
  cat("# Process genes for Panel 1\n")
  cat("genes <- c(", paste(paste0("\"", trimws(unlist(strsplit(user_inputs$heatmap_genes_panel1, ",|\\s+"))), "\""), collapse = ", "), ")\n")
  cat("genes <- toupper(trimws(genes))\n")
  cat("genes <- genes[genes %in% toupper(lazy_data$genes)]\n\n")
  
  cat("# Extract expression data\n")
  cat("expr_mat <- lazy_data$get_genes_expression_batch(genes, layer = 'X')\n")
  cat("if (is.null(expr_mat)) {\n")
  cat("  mat <- matrix(NA, nrow = lazy_data$n_cells, ncol = length(genes))\n")
  cat("  colnames(mat) <- genes\n")
  cat("} else {\n")
  cat("  mat <- expr_mat\n")
  cat("}\n\n")
  
  cat("# Process heatmap data\n")
  cat("heatmap_data <- process_heatmap_data(\n")
  cat("  mat = mat,\n")
  cat("  score_type = '", user_inputs$heatmap_score_panel1, "',\n")
  cat("  cell_group_mode = '", user_inputs$heatmap_cell_group_mode_panel1, "',\n")
  cat("  cluster_by = '", ifelse(is.null(user_inputs$heatmap_cluster_by_panel1), "", user_inputs$heatmap_cluster_by_panel1), "'\n")
  cat(")\n\n")
  
  cat("# Generate heatmap\n")
  cat("heatmap_plot <- render_heatmap(heatmap_data, 'Panel 1: Individual Genes')\n")
  cat("print(heatmap_plot)\n")
  cat("```\n\n")
  
  cat("🔗 **Complete Package:** https://github.com/yourusername/yourrepo\n\n")
}
```

```{r heatmap2-details, eval=!is.null(saved_plots$heatmap2), results='asis'}
if(!is.null(user_inputs$heatmap_gene_group_mode_panel2)) {
  cat("**Input Parameters:**\n\n")
  cat("- **Gene Group Mode:** ", user_inputs$heatmap_gene_group_mode_panel2, "\n")
  cat("- **Score Type:** ", user_inputs$heatmap_score_panel2, "\n")
  cat("- **Cell Grouping Mode:** ", user_inputs$heatmap_cell_group_mode_panel2, "\n")
  cat("- **Cluster/Color By:** ", ifelse(is.null(user_inputs$heatmap_cluster_by_panel2), "None", user_inputs$heatmap_cluster_by_panel2), "\n")
  
  # Show specific selections based on mode
  if(user_inputs$heatmap_gene_group_mode_panel2 == "pathways" && !is.null(user_inputs$heatmap_pathway_select_panel2)) {
    cat("- **Selected Pathways:** ", paste(user_inputs$heatmap_pathway_select_panel2, collapse = ", "), "\n")
  } else if(user_inputs$heatmap_gene_group_mode_panel2 == "custom_gmt" && !is.null(user_inputs$heatmap_gmt_sets_panel2)) {
    cat("- **Selected GMT Gene Sets:** ", paste(user_inputs$heatmap_gmt_sets_panel2, collapse = ", "), "\n")
  } else if(user_inputs$heatmap_gene_group_mode_panel2 == "manual" && !is.null(user_inputs$selected_manual_genesets)) {
    cat("- **Selected Manual Gene Sets:** ", paste(user_inputs$selected_manual_genesets, collapse = ", "), "\n")
  }
  cat("\n")
  
  cat("**Reproducible Code:**\n\n")
  cat("```r\n")
  cat("# Using the same setup as Panel 1:\n")
  cat("# library(yourpackagename)\n")
  cat("# lazy_data <- init_fast_zarr_h5ad(zarr_file)\n\n")
  
  if(user_inputs$heatmap_gene_group_mode_panel2 == "pathways") {
    cat("# Load pathway data (included in package or lazy_data)\n")
    cat("pathways <- lazy_data$pathways\n")
    if("ALL" %in% user_inputs$heatmap_pathway_select_panel2) {
      cat("gene_groups <- pathways  # All pathways selected\n")
    } else {
      cat("selected_pathways <- c(", paste(paste0("\"", user_inputs$heatmap_pathway_select_panel2, "\""), collapse = ", "), ")\n")
      cat("gene_groups <- pathways[selected_pathways]\n")
    }
  } else if(user_inputs$heatmap_gene_group_mode_panel2 == "custom_gmt") {
    cat("# Load GMT file (replace with your GMT file path)\n")
    cat("gmt_data <- parse_gmt_file('path/to/your/geneset.gmt')\n")
    if("ALL" %in% user_inputs$heatmap_gmt_sets_panel2) {
      cat("gene_groups <- gmt_data  # All GMT gene sets selected\n")
    } else {
      cat("selected_gmt <- c(", paste(paste0("\"", user_inputs$heatmap_gmt_sets_panel2, "\""), collapse = ", "), ")\n")
      cat("gene_groups <- gmt_data[selected_gmt]\n")
    }
  } else if(user_inputs$heatmap_gene_group_mode_panel2 == "manual") {
    cat("# Manual gene sets (replace with your gene sets)\n")
    cat("manual_genesets <- list(\n")
    if(!is.null(user_inputs$selected_manual_genesets)) {
      for(i in seq_along(user_inputs$selected_manual_genesets)) {
        cat("  '", user_inputs$selected_manual_genesets[i], "' = c('GENE1', 'GENE2', 'GENE3')")
        if(i < length(user_inputs$selected_manual_genesets)) cat(",")
        cat("\n")
      }
    }
    cat(")\n")
    cat("gene_groups <- manual_genesets\n")
  }
  
  cat("\n# Calculate gene set scores and create heatmap\n")
  cat("heatmap_data <- calculate_geneset_scores(\n")
  cat("  lazy_data = lazy_data,\n")
  cat("  gene_groups = gene_groups,\n")
  cat("  score_type = '", user_inputs$heatmap_score_panel2, "',\n")
  cat("  cell_group_mode = '", user_inputs$heatmap_cell_group_mode_panel2, "',\n")
  cat("  cluster_by = '", ifelse(is.null(user_inputs$heatmap_cluster_by_panel2), "", user_inputs$heatmap_cluster_by_panel2), "'\n")
  cat(")\n\n")
  
  cat("# Generate heatmap\n")
  cat("heatmap_plot <- render_heatmap(heatmap_data, 'Panel 2: Gene Sets')\n")
  cat("print(heatmap_plot)\n")
  cat("```\n\n")
  
  cat("🔗 **Complete Package:** https://github.com/yourusername/yourrepo\n\n")
}
```

```{r heatmap2-plot, eval=!is.null(saved_plots$heatmap2)}
include_graphics(normalizePath(saved_plots$heatmap2))
```

```{r gene-section-header, eval=!is.null(saved_plots$gene_main), results='asis'}
cat("### Gene Expression Analysis\n\n")
```

```{r gene-analysis-header, eval=!is.null(saved_plots$gene_main), results='asis'}
cat("#### Main Gene Analysis Plot\n\n")
```

```{r gene-analysis-details, eval=!is.null(saved_plots$gene_main), results='asis'}
# Add similar parameter display for gene analysis if you have the user_inputs values stored
cat("**Plot Details:**\n\n")
cat("This plot shows the main gene expression analysis results.\n\n")
```

```{r gene-analysis-plot, eval=!is.null(saved_plots$gene_main)}
include_graphics(normalizePath(saved_plots$gene_main))
```

```{r qc-section-header, eval=!is.null(saved_plots$qc_main), results='asis'}
cat("### Quality Control\n\n")
```

```{r qc-analysis-header, eval=!is.null(saved_plots$qc_main), results='asis'}
cat("#### Quality Control Plot\n\n")
```

```{r qc-analysis-details, eval=!is.null(saved_plots$qc_main), results='asis'}
# Add similar parameter display for QC if you have the user_inputs values stored
cat("**Plot Details:**\n\n")
cat("This plot displays the quality control metrics for the analysis.\n\n")
```

```{r qc-analysis-plot, eval=!is.null(saved_plots$qc_main)}
include_graphics(normalizePath(saved_plots$qc_main))
```

```{r canvas-section-header, results='asis'}
# Check if any canvas plots exist
canvas_plots <- saved_plots[grepl("canvas", names(saved_plots))]
if(length(canvas_plots) > 0) {
  cat("## Interactive Canvas Elements\n\n")
}
```

```{r scatterplot-canvas-header, eval=!is.null(saved_plots$scatterplot_canvas), results='asis'}
cat("### Scatterplot Canvas\n\n")
cat("#### Scatterplot Canvas\n\n")
```

```{r scatterplot-canvas-plot, eval=!is.null(saved_plots$scatterplot_canvas)}
include_graphics(normalizePath(saved_plots$scatterplot_canvas))
```

```{r scatterplot-canvas-text, eval=!is.null(saved_plots$scatterplot_canvas), results='asis'}
cat("\n\nThis image represents a static snapshot of the interactive scatterplot canvas generated in the application.\n")
```

```{r gene-canvas-header, results='asis'}
gene_canvases <- saved_plots[grepl("^gene_canvas_", names(saved_plots))]
if(length(gene_canvases) > 0) {
  cat("### Gene-Specific Canvas Plots\n\n")
  cat("The following static images represent snapshots of the interactive gene-specific canvas plots generated in the application:\n\n")
}
```

```{r gene-canvas-plots, results='asis'}
gene_canvases <- saved_plots[grepl("^gene_canvas_", names(saved_plots))]
if(length(gene_canvases) > 0) {
  for(canvas_name in names(gene_canvases)) {
    gene_name <- gsub("gene_canvas_", "", canvas_name)
    cat(sprintf("#### %s\n\n", gene_name))
    
    # Create a temporary variable for the current plot path
    current_plot <- gene_canvases[[canvas_name]]
    
    # Output the image using markdown syntax within asis
    cat(sprintf("![](%s)\n\n", normalizePath(current_plot)))
    
    cat(sprintf("This image represents a static snapshot of the interactive canvas for gene %s.\n\n", gene_name))
  }
}
```

## Data Processing Summary

```{r processing-summary, results='asis'}
total_plots <- length(saved_plots)
total_canvases <- length(saved_plots[grepl("^scatterplot_canvas|^gene_canvas_", names(saved_plots))])

cat("### Analysis Summary\n\n")
cat("- **Static plots generated (including canvas snapshots):** ", total_plots, "\n")
cat("- **Interactive canvases captured:** ", total_canvases, "\n")
cat("- **Report generation time:** ", format(timestamp, "%Y-%m-%d %H:%M:%S"), "\n\n")
```

## Technical Information

```{r tech-info}
cat("### Session Information\n\n")
cat("R version:", R.version.string, "\n")
cat("Platform:", R.version$platform, "\n")
cat("Report generated using: rmarkdown and knitr\n")
```

---

*This report was automatically generated from your Shiny application. For interactive features and real-time updates, please return to the application interface.*